Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-23 submission/Sze_Obesity_PeerJ_2016.Rmd
got a working Rmd to render

---
title: "Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome"
output:
  html_document:
    keep_md: yes
bibliography: submission/references.bib
---

@@

![Figure 1](results/figures/PrismaFlowGraph.png)\

@@

**Figure 3: Meta Analysis of the Relative Risk of Obesity Based on Shannon Diversity or Bacteroidetes/Firmicutes Ratio.**  Groups were divided for each study on high and low Shannon Diversity or Bacteroidetes/Firmicutes (B/F) ratio groups based on the median for that study. Red represents studies that used the 16S rRNA V4 region, yellow represents studies that used a V1-V3 approach, blue represents studies that used either a V1-V2 or just a V2 approach, and orange represents studies that used the V3-V5 region.  **A)** The overall pooled relative risk for Shannon Diversity was `r format(round(10^test3R$LogFC[1],2), nsmall=2)` with a P-value of `r format(round(RRSDPvalue$QMp, 2), nsmall=2)`.  **B)** The overall pooled relative risk for the B/F ratio was  `r format(round(10^test3BF$LogFC[1],2), nsmall=2)` with a P-value of `r format(round(RRBFPvalue$QMp, 2), nsmall=2)`.

@@

**Figure 4: Pooled Analysis of Shannon Diversity and B/F ratio by either Obesity Status or BMI Groups.**  **A)** Z-score Normalized Shannon Diversity and Obesity. There was a significant difference between non-obese (n = `r length(which(group.data.test$obese == "No"))`) and obese groups (n = `r length(which(group.data.test$obese == "Yes"))`) (P-value = `r signif(combZHTtest$p.value, 3)`). **B)** Z-score Normalized B/F Ratio and Obesity. There was no significant difference between the non-obese (n = `r length(which(group.data.test$obese == "No"))`) and obese (n = `r length(which(group.data.test$obese == "Yes"))`) group based on B/F ratio (P-value = `r signif(combZLogBFTtest$p.value, 3)`).

>>>>

---
title: "Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome"
output:
  html_document:
    keep_md: yes
bibliography: reference.bib
---

@@

![Figure 1](../results/figures/Figure_1.png)\

@@

**Figure 3: Meta Analysis of the Relative Risk of Obesity Based on Shannon Diversity or Bacteroidetes/Firmicutes Ratio.**  Groups were divided for each study on high and low Shannon Diversity or Bacteroidetes/Firmicutes (B/F) ratio groups based on the median for that study. Red represents studies that used the 16S rRNA V4 region, yellow represents studies that used a V1-V3 approach, blue represents studies that used either a V1-V2 or just a V2 approach, and orange represents studies that used the V3-V5 region.  **A)** The overall pooled relative risk for Shannon Diversity was `r format(round(RR_composite['shannon', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['shannon', 'p_value']), nsmall=2)`.  **B)** The overall pooled relative risk for the B/F ratio was  `r format(round(RR_composite['bf_ratio', 'rr'],2), nsmall=2)` with a P-value of `r format(round(RR_composite['bf_ratio', 'p_value'], 2), nsmall=2)`.

@@

**Figure 4: Pooled Analysis of Shannon Diversity and B/F ratio by either Obesity Status or BMI Groups.**  **A)** Z-score Normalized Shannon Diversity and Obesity. There was a significant difference between non-obese (n = `r length(which(alpha.data.ALL$obese == FALSE))`) and obese groups (n = `r length(which(alpha.data.ALL$obese == TRUE))`) (P-value = `r format(round(alpha_composite.summary['shannon', 'composite_p'], 4), nsmall=4)`). **B)** Z-score Normalized B/F Ratio and Obesity. There was no significant difference between the non-obese (n = `r length(which(alpha.data.ALL$obese == FALSE))`) and obese (n = `r length(which(alpha.data.ALL$obese == TRUE))`) group based on B/F ratio (P-value = `r format(round(alpha_composite.summary['bf_ratio', 'composite_p'], 2), nsmall=2)`).
